% Created 2024-10-19 Sat 18:37
% Intended LaTeX compiler: xelatex
\documentclass[11pt]{article}
\usepackage[mathletters]{ucs}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=0.5in]{geometry}
\author{Shane Mulligan}
\date{\textit{<2024-10-19 Sat>}}
\title{New Testament Greek study}
\hypersetup{
 pdfauthor={Shane Mulligan},
 pdftitle={New Testament Greek study},
 pdfkeywords={faith christianity},
 pdfsubject={},
 pdfcreator={Emacs 29.1.50 (Org mode 9.6.8)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{NT Greek study}
\label{sec:orgcea93f4}

\subsection{Question}
\label{sec:org368a1b4}

I'd like to understand the Greek behind the phrase \uline{in the teaching of Christ}.
Because I'm interested in whether the phrase \uline{teaching of Christ} refers to the teachings that Christ
taught including His teachings before His death, burial and resurrection, or
if it the phrase is also talking about the doctrine surrounding what is known about Christ.
My guess is both, but I'd like to understand the Greek a bit better.

\begin{quote}
\textbf{II John 1:9} - Everyone who goes on ahead and does not abide \uline{in the teaching of Christ}, does not have God. Whoever abides in the teaching has both the Father and the Son. (ESV)
\end{quote}

\subsection{Case}
\label{sec:org792cb64}

\begin{verbatim}
 1  interrogative
 2      /ˌɪntəˈrɒɡətɪv/
 3      adjective
 4      having the force of a question.
 5      "a hard, interrogative stare"
 6  
 7  transitive verb
 8      A verb that entails one or more transitive
 9      objects, for example, 'enjoys' in Amadeus
10      enjoys music.
11  
12      This contrasts with intransitive verbs,
13      which do not entail transitive objects,
14      for example, 'arose' in Beatrice arose.
\end{verbatim}

Notes from \url{https://en.wikipedia.org/wiki/Grammatical\_case}:

\begin{itemize}
\item \textbf{N (Nominative)}
\begin{itemize}
\item \texttt{Indicates}: Subject of a finite verb
\item \texttt{Sample case words}: \uline{we}
\item \texttt{Sample sentence}: \uline{We} went to the store.
\item \texttt{Interrogative}: Who or what?
\item \texttt{Notes}: Corresponds to English's subject pronouns.
\end{itemize}
\item \textbf{V (Vocative)}
\begin{itemize}
\item \texttt{Indicates}: Addressee
\item \texttt{Sample case words}: \uline{John}
\item \texttt{Sample sentence}:
\begin{itemize}
\item \uline{John}, are you all right?
\item Hello, \uline{John}!
\item O John, how are you! (archaic)
\end{itemize}
\item \texttt{Interrogative}:
\item \texttt{Notes}: Roughly corresponds to the archaic use of "O" in English.
\end{itemize}
\item \textbf{A (Accusative)}
\begin{itemize}
\item \texttt{Indicates}: Direct object of a transitive verb
\item \texttt{Sample case words}: \uline{us}, \uline{for us}, \uline{the (object)}
\item \texttt{Sample sentence}:
\begin{itemize}
\item The clerk remembered \uline{us}.
\item John waited \uline{for us} at the bus stop.
\item Obey \uline{the law}.
\end{itemize}
\item \texttt{Interrogative}: 
\begin{itemize}
\item Whom or what?
\end{itemize}
\item \texttt{Notes}: Corresponds to English's object pronouns and preposition for construction before the object, often marked by a definite article the. Together with dative, it forms modern English's oblique case.
\end{itemize}
\item \textbf{G (Genitive)}
\begin{itemize}
\item \texttt{Indicates}: Possessor of another noun
\item \texttt{Sample case words}: \uline{'s}, \uline{of (the)}
\item \texttt{Sample sentence}: 
\begin{itemize}
\item \uline{John's} book was on the table.
\item The pages \uline{of the book} turned yellow.
\item The table is made \uline{out of wood}.
\end{itemize}
\item \texttt{Interrogative}: Whose? From what or what of?
\item \texttt{Notes}: Roughly corresponds to English's possessive (possessive determiners and pronouns) and preposition of construction.
\end{itemize}
\item \textbf{D (Dative)}
\begin{itemize}
\item \texttt{Indicates}: Indirect object of a verb
\item \texttt{Sample case words}: \uline{us}, \uline{to us}, \uline{to the (object)}
\item \texttt{Sample sentence}:
\begin{itemize}
\item The clerk gave \uline{us} a discount.
\item The clerk gave a discount \uline{to us}.
\item According \uline{to the law\ldots{}}
\end{itemize}
\item \texttt{Interrogative}: Whom or to what?
\item \texttt{Notes}: Corresponds to English's object pronouns and preposition to construction before the object, often marked by a definite article the. Together with accusative, it forms modern English's oblique case.
\end{itemize}
\end{itemize}

\subsubsection{Example}
\label{sec:orgc680dc9}
\url{https://biblehub.com/interlinear/2\_john/1-9.htm}

\begin{verbatim}
1  tou
2  3588
3  tou
4  τοῦ
5   -
6  Art-GMS
\end{verbatim}

\begin{itemize}
\item G - \href{https://en.wikipedia.org/wiki/Grammatical\_case}{Genitive}
\item M - \href{https://en.wikipedia.org/wiki/Grammatical\_case}{Masculine}
\item S - \href{https://en.wikipedia.org/wiki/Grammatical\_case}{Singular}
\end{itemize}
\end{document}